\chapter{Directory tree}
%
Following all the files provided with \NAME package, with its location, is 
shown.
%
The files autogenerated during the configuration, build and install processes 
are not shown.
%
The purpose of some of these files and folders is explained later.

\vspace{0.5cm}
\rule{\textwidth}{1pt}
\vspace{0.5cm}
\input{tree_py}
\vspace{0.5cm}
\rule{\textwidth}{1pt}
\vspace{0.5cm}

All the files called ``\texttt{CMakeLists.txt}'', ``\texttt{*.cmake}'', or 
included in a ``cMake'' folder are designed to let cmake to configure the 
package for the build and installation process, please refer to section 
\ref{s:install} to learn more about cmake.
%
More specifically, the files called ``\texttt{CMakeLists.txt}'' are the ones 
where the instructions for cmake are written, while the other ones are 
templates that cmake is conveniently reading and editing.

In the folder ``\texttt{doc}'' the main documentation files can be found.
%
Inside can be found the subfolder ``\texttt{userManual}'', where this manual 
and all the resources to build it are placed.
%
During the cmake configuration, if the flag \textbf{AQUAGPUSPH\_BUILD\_DOC} 
is  activated (see section \ref{sss:install:cmake}), Doxygen documentation 
will be  build as well, placing it in the folder ``\texttt{doc/Doxygen/html}'' 
(see section \ref{ss:aquagpusph:general}).

In the folders ``\texttt{src}'' and ``\texttt{include}'' the source codes of 
\NAME can be found.
%
Note that the OpenCL codes, which are not included into the \NAME compiled 
binary file, are placed inside ``\texttt{resources}'' folder.
%
A CodeBlocks project is provided for the developers in the file 
``CodeBlocks/AQUAgpusph.cbp''.
%
However, it is strongly recommended to use cmake to perform compilations.

In the folder ``\texttt{examples}'' the examples provided with \NAME package 
are placed.
%
To setup the examples you should activate the flag 
\textbf{AQUAGPUSPH\_BUILD\_EXAMPLES}.
%
The examples available depends on whether the 2D version or 3D version is 
built (see section \ref{sss:install:cmake}).
%
When 2D version is build (\textbf{AQUAGPUSPH\_3D=OFF}) the following examples 
will be generated:
%
\begin{itemize}
	\item ``\texttt{examples/LateralWater\_1x\_DeLeffe}''
	\item ``\texttt{examples/LateralWater\_1x\_Fix}''
	\item ``\texttt{examples/LateralWater\_1x\_Ghost}''
	\item ``\texttt{examples/lobovsky\_etal\_jfs\_2014}''
\end{itemize}
%
While for the 3D version (\textbf{AQUAGPUSPH\_3D=ON}) the following examples 
will be generated:
%
\begin{itemize}
	\item ``\texttt{examples/perezrojas\_etal\_stab\_2012}''
\end{itemize}

Note that both, 3D and 2D versions, may be installed together in the same 
system.
%
After building the examples a bash script ``\texttt{run.sh}'' is provided for 
each one.
%
Call this script with the option ``\texttt{--help}'' to know how to run and 
track them.