\subsection{GiD formatted file}
\label{sss:partsFile:GiD}
%
\NAME accepts particles distribution in GiD mesh format. Mesh
points will be used as the particles positions, with the
provided fields. GiD format must provide following fields:
%
\begin{enumerate}
	\item \textbf{$x$} (Mandatory): X coordinate $[\mbox{m}]$.
	\item \textbf{$y$} (Mandatory): Y coordinate $[\mbox{m}]$.
	\item \textbf{$z$} (Mandatory, only for 3D): Z coordinate $[\mbox{m}]$.
	\item \textbf{$w$} (Mandatory, only for 3D): Usually $w=1 [\mbox{m}]$.
	\item \textbf{$n_x$} (Mandatory): X normal component. Fluid particles can have null normal.
	\item \textbf{$n_y$} (Mandatory): Y normal component. Fluid particles can have null normal.
	\item \textbf{$n_z$} (Mandatory, only for 3D): Z normal component. Fluid particles can have null normal.
	\item \textbf{$n_w$} (Mandatory, only for 3D): Usually $n_w=0$.
	\item \textbf{$v_x$} (Mandatory): X velocity component $[\mbox{m/s}]$.
	\item \textbf{$v_y$} (Mandatory): Y velocity component $[\mbox{m/s}]$.
	\item \textbf{$v_z$} (Mandatory, only for 3D): Z velocity component $[\mbox{m/s}]$.
	\item \textbf{$v_z$} (Mandatory, only for 3D): Usually $v_w=0 [\mbox{m/s}]$.
	\item \textbf{$m$} (Mandatory): Mass if it is a fluid or fix particle $[\mbox{kg}]$, area if it is a wall element $[\mbox{m}^2]$.
	\item \textbf{$imove$} (Optional): Moving flag. $imove > 0$ for all fluid particles, $imove < 0$ for fixed
	particles or vertexes ($imove = 0$ is reserved for sensors).
	\item \textbf{$\rho$} (Optional): Density $[\mbox{kg/m}^3]$.
	\item \textbf{$c_S$} (Optional): Sound speed $[\mbox{m/s}]$. Sound speed must be selected, at least, 10
	times greater than maximum expected fluid velocity.
	\item \textbf{$h$} (Optional): Kernel characteristic height $[\mbox{m}]$.
\end{enumerate}
%
Fields are really similar to the introduced at \ref{sss:partsFile:ASCII} section about the ASCII formatted input.
%