\chapter{Install \NAME}
\label{s:install}
%
\section{General}
%
\NAME can be downloaded from
%
\begin{center}
\url{http://canal.etsin.upm.es/aquagpusph/descargas.php}
\end{center}
%
The process to configure, build and install is described below. The files
uploaded to this web page are the latest stable version, but optionally
you can download the developers version, that has more fresh features, but
can carry some bugs and unstabilities. Developers version is allocated in
\href{https://github.com/}{github}, so you must have git installed on your
system to access to the source code. To download the developers package
version execute
%
\begin{verbatim}
git clone git://github.com/jlcercos/aquagpusph.git
\end{verbatim}
%
that will generate a folder called ``aquagpusph'' with the package inside.\rc
%
The instructions included below are valid for both the stable and the
developers versions, but some additional dependencies and configuration can
be missed.\rc
%
For the moment no specific GNU/Linux distributions installable packages have
been created.
%
\section{Dependencies}
%
\NAME has some dependencies that must be installed before. Almost dependencies
are mandatory, but exist other dependencies that can be optionally ignored
depending on the needed capabilities on \NAME built program.\rc
%
Dependencies are classified in 4 categories therefore:
%
\begin{enumerate}
	\item Mandatory: \NAME needs the dependency available on system in order to
	run.
	\item Optional: If dependency is not available, \NAME can be built, but some
	features will be disabled.
	\item Recommended: If dependency is not available, \NAME can be built with
	all the features, but some
	additional package characteristics may not run.
	\item Suggested: \NAME can have some synergies with other softwares, for
	preporcessing or postprocessing for instance.
\end{enumerate}
%
In table \ref{tables:install:dependencies} you can see the list of dependencies
required. Each dependency can require more other dependencies that will not be
documented. Take into account the following considerations:
%
\begin{enumerate}
	\item OpenCL is a little bit special dependency due to is really hardware
	depending, therefore at the web page only OpenCL specification will found.
	We encourage you to contact your hardware provider in order to know the
	best way to install it.
	\item NCurses can be used to perform smart screen output, that can revert
	on slightly reduced computational time. Any relevant functionality will
	be lost if \NAME is compiled without NCurses support therefore.
	\item VTK support is actually on development, so it can be safely discarded,
	but future versions on \NAME can require it.
	\item H5Part is the main \NAME output format, that is post-processable with
	Paraview. It's strongly recommended to have H5Part support on \NAME, but if
	you don't plain to use Paraview for post-processing cases you can consider
	don't install this library. If H5Part parallel version is installed, a MPI
	must be installed too (OpenMPI has been tested, but other platforms can be
	theoretically used). Must be noticed that \NAME is not a MPI oriented
	software, so please, don't try to perform parallel execution with
	\textit{mpirun}.
	\item Doxygen and Graphviz are only needed if you want to build Doxygen
	developers documentation. This documentation is mainly oriented to developers,
	but can be really useful for users in some number of cases, so is recommended
	to build it.
	\item Regarding Paraview, even though almost Linux distributions have a
	package to easily install it, if you want to use it to postprocess \NAME
	simulations probably you want to add H5Part files loading module, and then
	probably you want to build Paraview from sources.
\end{enumerate}
%
\begin{table}[h!b!p!]\small
	\centering
	\begin{tabular}{| c | c | c | }
		\hline
		\cellcolor[rgb]{0.7,0.7,0.7}Dependency &\cellcolor[rgb]{0.7,0.7,0.7}Status &\cellcolor[rgb]{0.7,0.7,0.7}Web page\\
		\hline
		CMake    & Mandatory   & \url{http://www.cmake.org} \\
		\hline
		xerces-c & Mandatory   & \url{http://xerces.apache.org/xerces-c} \\
		\hline
		Python   & Mandatory   & \url{http://www.python.org} \\
		\hline
		OpenCL   & Mandatory   & \url{http://www.khronos.org/opencl} \\
		\hline
		Ncurses  & Optional    & \url{http://www.gnu.org/software/ncurses/ncurses.html} \\
		\hline
		VTK      & Optional    & \url{http://www.vtk.org} \\
		\hline
		H5Part   & Optional    & \url{http://vis.lbl.gov/Research/H5Part} \\
		\hline
		OpenMPI  & Optional    & \url{http://www.open-mpi.org} \\
		\hline
		Doxygen  & Recommended & \url{http://www.doxygen.org} \\
		\hline
		Graphviz & Recommended & \url{http://www.graphviz.org} \\
		\hline
		gnuplot  & Suggested   & \url{http://www.gnuplot.info} \\
		\hline
		ParaView & Suggested   & \url{http://www.paraview.org/} \\
		\hline
	\end{tabular}
	\caption{\NAME dependencies.}
	\label{tables:install:dependencies}
\end{table}
%
\section{Install}
%
\subsection{General}
%
\NAME use \href{http://www.cmake.org}{CMake} to the configure, build and install
process. CMake installation process is performed in 3 steps therefore:
%
\begin{enumerate}
	\item \textbf{CMake configuration}: In this stage main options and features
	that the built version of \NAME will have.
	\item \textbf{Compilation}: In this step the source code is compiled into a
	binary ready to be launched.
	\item \textbf{Install}: This step is optional, aiming to install the software
	on the system in order to be available for all the users of the computer.
\end{enumerate}
%
To perform the CMake configuration process 2 ways are described.
%
\subsection{CMake configuration}
\label{sss:install:cmake}
%
To start configuring CMake you can run the following command on the folder where
you downloaded \NAME sources:
%
\begin{verbatim}
cmake .
\end{verbatim}
%
That will configure \NAME with default options. You can modify some options, for
instance, to change installation prefix from $\mbox{/usr/local}$ to $\mbox{/usr}$
folder, and build Release version (If not build type is selected, Release version
will set by default), you can launch following command:
%
\begin{verbatim}
cmake . -D CMAKE_INSTALL_PREFIX:PATH=/usr -D CMAKE_BUILD_TYPE:STRING=Release
\end{verbatim}
%
In \url{http://www.cmake.org/Wiki/CMake_Useful_Variables} web page you can find a
list with the most commonly CMake used options. Also \NAME provides some additional
options:
%
\begin{enumerate}
	\item \textbf{AQUAGPUSPH\_3D}: ON to build 3D \NAME version, OFF to build 2D
	version. \NAME 2D and 3D versions can be installed on the same system. Be
	mindful that 3D version must not be used to perform 2D simulations.
	\item \textbf{AQUAGPUSPH\_BUILD\_DOC}: ON to build
	\href{http://www.doxygen.org}{Doxygen} developers documentation, OFF otherwise.
	Requires \href{http://www.doxygen.org}{Doxygen} and
	\href{www.graphviz.org}{Graphviz} packages installed.
	\item \textbf{AQUAGPUSPH\_BUILD\_EXAMPLES}: ON to generate the examples.
	Generated examples are the associated to the selected 2D/3D version.
	\item \textbf{AQUAGPUSPH\_ENABLE\_MPI}: ON to enable MPI support, OFF otherwise.
	Actually \NAME don't use MPI, but if you installed H5Part with MPI support, you
	need to build \NAME with MPI support too.
	\item \textbf{AQUAGPUSPH\_USE\_H5PART}: ON to build \NAME with H5Part output
	support, OFF otherwise. It's strongly recommended activate H5Part support, but
	require H5Part library installed.
	\item \textbf{AQUAGPUSPH\_USE\_NCURSES}: ON to build \NAME with NCurses output
	terminal, OFF otherwise. NCurses has more efficient screen streamed functionality,
	so you can win some performance using it.
	\item \textbf{AQUAGPUSPH\_USE\_TECPLOT}: ON to build \NAME with Tecplot output
	support, OFF otherwise. Since Tecplot output is an ASCII format, don't cause
	additional dependencies, so let it ON, but is strongly recommended don't use
	this output format, that is not actively developed.
	\item \textbf{AQUAGPUSPH\_USE\_VTK}: ON to build \NAME with Tecplot output
	support, OFF otherwise. Actually \NAME don't use this output format, but will
	developed on future. Deactivate it if you detect troubles.
\end{enumerate}
%
\subsection{CMake configuration with ccmake}
%
I order to simplify the process you can use ccmake\footnote{Or eventually CMake-GUI}
to configure \NAME with a more friendly user interface (Of course you must install
ccmake before). Simply launch the command:
%
\begin{verbatim}
ccmake .
\end{verbatim}
%
If you did not configure \NAME before, an empty cache page will shown up, press
\textbf{'c'} key to perform initial default configuration. After some seconds working,
errors, warnings, and most relevant selected options report will be returned; press
\textbf{'e'} key to continue.\rc
%
Now some options are shown in order to allow you to edit them. In case you did not
receive errors at configuration process, you only need to set
\textbf{AQUAGPUSPH\_ENABLE\_MPI} according to H5Part library, otherwise you may solve
the problems or disable related features if possible.\rc
%
Probably you want to edit CMAKE\_INSTALL\_PREFIX too. Take care about
CMAKE\_BUILD\_TYPE, Debug mode is a lot of more resources consuming and slow, it's
strongly recommended to let Release mode for almost users.\rc
%
After this, press \textbf{'c'} key in order to configure the package again. Repeat the
process until no new options are shown (that are marked with an asterisk), and no more
errors are reported. At this point ccmake will offer generating final project pressing
\textbf{'g'} key.\rc
%
Same options introduced in \ref{sss:install:cmake} can be set using ccmake.
%
\subsection{Compilation}
%
After configuration process you can start the compilation in order to create the binary.
You can launch the following command:
%
\begin{verbatim}
make all
\end{verbatim}
%
Since \NAME build process is not really time consuming parallel compiling process is not
generally needed, but of course you can set several processors building simultaneously.
For instance, if you want to use 8 cores you can type:
%
\begin{verbatim}
make -j8
\end{verbatim}
%
Additionally, if you want to get more info about the building process, you can use
VERBOSE flag:
%
\begin{verbatim}
make VERBOSE=1
\end{verbatim}
%
This will report the command executed to compile or generate each file.
%
\subsection{Install}
%
\NAME can be used without installing it, see generated examples to learn more about this,
but if \NAME must be provided to several users probably you want to install it typing:
%
\begin{verbatim}
make install
\end{verbatim}
%
Note that depending the selected installation folder you may need administrative permissions.
%