\chapter{Running \NAME}
\label{s:running}
%
\section{Launching simulation}
\label{ss:running:launching}
%
In order to launch \NAME simulation you need to execute the program
specifying the XML definition file in a command line. If you have
installed \NAME in a folder present on the PATH environment variable
you can launch a 3D simulation typing:
%
\begin{alltt}
AQUAgpusph -i \emph{PathToXML}
\end{alltt}
%
or
%
\begin{alltt}
AQUAgpusph2D -i \emph{PathToXML}
\end{alltt}
%
for 2D simulations.\rc
%
\NAME accepts several command line options. You can get a complete list
and description of them in the help page (`-h/--help' help option). If
the `-i/--input' option is not provided, Input.xml file will be selected
as the XML case definition file, so must exist in the execution folder.
You can consider use '-n/--no-reassembly' since output files reassembly
can be a really time and hard-disk consuming operation, and simply
unuseful if the simulation has been ran without interruptions.\rc
%
You can start a simulation from previous output file. If you plan to perform
the simulation in several runs, consider not perform the reassembly before
the last execution. Also you will need to set options according (see section
\ref{sss:XML:Settings} to learn more about this).\rc
%
\NAME execution can be stopped using `c' key. When `c' key event is detected
simulation will be stopped at the end of the active time step, and output
saved and closed correctly.\rc
%
Eventually you can stop the simulation pressing `Ctrl'+`c', but then the
simulation will stop immediately, and can result in output unreadable
files\footnote{H5Part output will be surely broken}.
%
\section{Tracking simulation}
\label{ss:running:tracking}
%
\subsection{General}
%
\NAME prints the log information in 2 different ways, on the screen and in a
log HTML file. Both of them have similar content, and can be controlled
independently.\rc
%
\subsection{Screen log information}
\label{sss:running:screenlog}
%
The screen real time output can be controlled in the settings configuration
section, see chapter \ref{sss:XML:Settings} for details.\rc
%
The screen output will report some data organized in groups:
%
\begin{itemize}
	\item Simulation progress
	\begin{itemize}
		\item Simulation time $[\mbox{s}]$.
		\item Simulation time step $[\mbox{s}]$.
		\item Percentage of the simulation accomplished.
		\item Last output frame printed.
		\item Estimated Time to Arrive $[\mbox{s}]$.
	\end{itemize}
	\item Profile data (Only Debug version)
	\item Calculation server memory
	\begin{itemize}
		\item Number of particles.
		\item Number of cells.
		\item Allocated memory $[\mbox{bytes}]$.
	\end{itemize}	
	\item Energy data
	\begin{itemize}
		\item Momentums $[\mbox{N} \cdot \mbox{s}]$
		\item Angular momentums $[\mbox{N} \cdot \mbox{m s}]$
		\item Kinetic energy $[\mbox{J}]$
		\item Potential energy $[\mbox{J}]$
		\item Total energy $[\mbox{J}]$
	\end{itemize}	
	\item Events registry
\end{itemize}
%
Depending on your settings the ``Energy data'' group will be printed
more often, or eventually not printed. Actually energy data is not
computed on GPU, which implies a significant time consuming process
and it's strongly recommended to decrease print rate as much as possible.\rc
%
In the other hand, when \NAME has computed the energy data in a certain
time step, it does not recompute it until new step is called, so you can
consider to set that all energy data outputs to be performed on the same
instant (see the sections \ref{sss:running:logfile} and
\ref{ss:running:energyoutput} to learn more about this).\rc
%
\NAME also shows in real time an events registry, where some relevant
messages are shown. Messages are classified in 4
categories\footnote{Colors are only actives if \NAME has been built with
NCurses support, see chapter \ref{s:install} for details.}:
%
\begin{enumerate}
	\item \textbf{Terminal output}: Initialization and closing information.
	\item \textbf{White}: Relevant information.
	\item \textbf{Orange}: Warning messages.
	\item \textbf{Red}: Error messages.
\end{enumerate}
%
In section \ref{sss:running:messages} you can find a list of the messages
that you can expect from the simulation, and the possible causes of them.
%
\subsection{HTML log file}
\label{sss:running:logfile}
%
Depending on the settings discussed on the section \ref{sss:XML:Timing},
\NAME can be configured to print a log HTML file ``Log.html''\footnote{If
prefix is not set as command line option. You can set a prefix that will
be inserted at the start of all the output file names}. The log file contains
useful information to to track it remotely and in order to know and
preserve all incidents and remarks associated with the simulation.\rc
%
HTML log file contains information classified in 3 categories:
%
\begin{enumerate}
	\item \textbf{Black}: Relevant information.
	\item \textbf{Orange}: Warning messages.
	\item \textbf{Red}: Error messages.
\end{enumerate}
%
In section \ref{sss:running:messages} you can find a list with some relevant
messages that you can get on the log HTML file. Also Information about date
and time, and printed output files will be included on this file.
%
\subsection{Messages glossary}
\label{sss:running:messages}
%
\NAME reports several messages on real time. In this section we show all
the messages that can be shown, with description, source, and possible
solution if proceed.\rc
%
The messages have the following structure:
%
\begin{alltt}
[\emph{TYPE} (T=\emph{TIME}s, Step=\emph{STEP})] (\emph{METHOD}): \emph{MESSAGE}
\end{alltt}
%
\textit{TYPE} is the type of message, that can be INFO, WARNING, or ERROR;
\textit{TIME} is the simulation time where the event has been registered;
\textit{STEP} is the simulation time step where the event has been registered;
\textit{METHOD} is the \NAME routine that registered the event; \textit{MESSAGE}
is the description of the event.\rc
%
The list of events that you can obtain during the \NAME execution are:
%
\input{errorMsg}
\input{warningMsg}
\input{infoMsg}
%
